Dark matter halo concentrations with a bayesian approach

### 2014-07-31 paper/article.tex
new plots

\begin{figure}
\caption{FIXME: Mass profile of a halo}
\end{figure}

@@

In Figure \ref{fig:results_mocks} we show the integrated distribution
percentual difference between the concentration measured with our
fitting method $c_{out}$ in comparison with the concentration used to
generate the mock halos, $c_{in}$, $D=(c_{in}-c_{out})/c_{in}$.

@@

\subsection{Comparison against other methods}

\subsection{Concentration as a function of halo mass}

\subsection{Implication for comparisons against observations}

\section{Conclusions}
\label{sec:conclusions}

>>>>

\begin{figure}
\begin{center}
  \includegraphics[width=0.48\textwidth]{nfw_normalized.pdf}
\end{center}
\caption{Mass profiles of several haloes with different concentrations
    \label{fig:profiles}}
\end{figure}

@@

In Figure \ref{fig:results_mocks} we show the integrated distribution
percentual difference between the concentration measured with our
fitting method $c_{out}$ in comparison with the concentration used to
generate the mock halos, $c_{in}$, $D=(c_{in}-c_{out})/c_{in}$. Then we can see that as the number of particles increases, the curve becomes more pronounced at 0. Showing that for most of the halos $c_{in}$ is very similar to $c_{out}$.

@@

\subsection{Comparison against other methods}
FIXME: Ask to Jaime, Differences with BDM
\subsection{Concentration as a function of halo mass}
FIXME: Add plots and interpretation, Matches with BDM
\subsection{Implication for comparisons against observations}
FIXME: Ask to Jaime

\section{Conclusions}
\label{sec:conclusions}
FIXME: Ask to Jaime
